### 2025-04-30 lecturenotes_aima203/ch1_aima203.tex
Correct significant digits
exercise ch1

\item Zeros to the right of the last non-zero digit (trailing zeros) in a number with the decimal point are significant. The number $320.$ has three significant digits.

\item When the decimal point is not written, the trailing zeros are not significant. The number $4500$ may be written as $45 \times 10^2$ has two significant digits. However, the number $4500.0$ has four significant digits.

@@

\subsection{Absolute errors of Sum, Product and Product}
Suppose \(a_1\) and \(a_2\) are two approximate values of a number with their absolute errors \(E_A^1\) and \(E_A^2\) respectively.

@@

\end{enumerate}

>>>>

\item Zeros to the right of the last non-zero digit (trailing zeros) in a number with the decimal point are significant. The number $320.$ has three significant digits, and $320.00$ has five significant digits.

\item When the decimal point is not written, the trailing zeros are not significant. The number $4500$ may be written as $45 \times 10^2$ has two significant digits. However, the number $4500.0$ has five significant digits.

@@

\subsection{Absolute errors of Sum, Product and Product}
Suppose \(a_1\) and \(a_2\) are approximate values of two  numbers, with their absolute errors \(E_A^1\) and \(E_A^2\) respectively.

@@

\item Find the absolute error in the product $uv$, where $u=4.536$ and $v=1.32$, the numbers being correct up to the digits given. Find the relative error of the quotient $u/v$ as well.
\end{enumerate}
